### 2016-11-02 Hhh/Hhh.tex
Adding some more stuff

\section{Datasets and Monte Carlo samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 $p-p$ 
running period of the LHC. 
Signal and background events were generated using several different MC event generators. The \texttt{MadGraph}
\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
events. In addition to samples with a mixture of jet multiplicities ('inclusive' samples), samples binned in jet multiplicity
were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
in signal regions with multiple jets. The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all MC samples to model additional
interactions.

@@

Figure \ref{fig:Hhh_selection_kinematics_mt} shows some of the kinematic variables 
of di-\Pgt candidates in the \mutau channel
\begin{figure}[h!]
\begin{center}
 \subfloat[Muon \pT]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_mt_2012.pdf}}
  \subfloat[Hadronic \Pgt \pT ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_mt_2012.pdf}}~\\
  \subfloat[Muon $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_mt_2012.pdf}}
  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_mt_2012.pdf}}~\\

\end{center}
\caption{Plots of muon and hadronic \Pgt \pT and $\eta$ in the \mutau channel.}
\label{fig:Hhh_selection_kinematics_mt}
\end{figure}

@@

Figure \ref{fig:Hhh_selection_kinematics_et} shows some of the kinematic variables 
of di-\Pgt candidates in the \etau channel
\begin{figure}[h!]
\begin{center}
 \subfloat[Electron \pT]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_et_2012.pdf}}
  \subfloat[Hadronic \Pgt \pT ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_et_2012.pdf}}~\\
  \subfloat[Electron $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_et_2012.pdf}}
  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_et_2012.pdf}}~\\

\end{center}
\caption{Plots of electron and hadronic \Pgt \pT and $\eta$ in the \etau channel.}
\label{fig:Hhh_selection_kinematics_et}
\end{figure}

\subsection{Categorisation}
\label{sec:hhh_selection_categories}
ADD b-jet plots?
In both channels an selection on the transverse mass \mT between the electron/muon
and missing transverse energy, defined as in equation \ref{eqn:hhh_selection_mt}, is applied.

\begin{equation}\label{eqn:hhh_selection_mt}
m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}
\end{equation}

In this eqation \pT is the transverse momentum of the electron or muon, and $\Delta\phi$ the angle
between the light lepton and the missing transverse energy. The \mT distributions for the \etau
and \mutau channels, using the selections as
described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
is shown in figure \ref{fig:Hhh_selection_mt}

@@

\section{Data to Monte Carlo correction factors}
\label{sec:hhh_datamc}
Monte Carlo samples are used for the estimation of some of the backgrounds and the signal, 
and it is therefore important to correct for any mismodelling. The data to Monte Carlo
correction factors used for this are estimated in dedicated control regions.

A reweighting is applied to make the pile--up distribution in Monte Carlo
match the distribution observed in data.DESCRIPTION

Data and Monte Carlo identification, isolation, and trigger efficiencies
are measured for electrons, muons and hadronic taus. The difference between
the efficiencies in data and Monte Carlo are applied to Monte Carlo events as a
scale factor $SF = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.

@@

In the \etau channel a data to Monte Carlo scale factor is applied
to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
fake rate between data and MC. DERIVED HOW

To correct for the difference in b--tagging efficiency and light jet mis--tagging
rates between data and Monte Carlo \pT and $\eta$ dependent scale factors are 
derived using the method described in \cite{BTV8TeV}. There are separate scale factors for 
b-/c- jets and light jets. There are multiple possible ways to apply these
scale factors, for this analysis this is done through a promote/demote method.

In this method a demotion or promotion probability is assigned to every
jet as in equation \ref{eqn:promotedemote}.

\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1}
\end{align}.

In this equation $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b--tagging efficiency in Monte Carlo events for the type of jet (light, b- or c-)
in consideration.

@@

Before the fit, from the mass constraint we have (equation \ref{eqn:kinfit_prefit})

\begin{align}\label{eqn:kinfit_prefit}
m_{h}^2 &= E_{h}^2 - \vec{p_{h}}^2 = (E_{b1}+E_{b2})^2 - (\vec{p_{b1}} + \vec{p_{b2}})^2 \notag\\
& = 2E_{b1}E_{b2} + m_{b1}^2 +m_{b2}^2 - 2\vec{p_{b1}}\vec{p_{b2}} \notag\\
& = m_{b1}^2 +m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta_{b2}})\notag\\
&\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}
\end{align}

When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{b1}}\vec{\beta_{b2}})$ 
and equation \ref{eqn:gamma_def}:

\begin{equation}\label{eqn:gamma_def}
\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2}
\end{equation}

We get:

\begin{align}\label{eqn:kinfit_variation}
m_h^2 &= m_{b1}^2 + m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta{b2}}\notag\\
&= m_{b1}^2 +\frac{E_{b2,fit}^2}{\gamma_{b2}^2} +2\mathcal{A}E_{b1}E_{b2,fit}\notag\\
\Rightarrow E_{b2}^{fit}& = \frac{(-2E_{b1}\mathcal{A} + \sqrt{4E_{b1}^2\mathcal{A} - 4(m_{b1}^2-m_{h}^2)\gamma_{b2}^{-2}})\gamma_{b2}^2}{2}\notag\\
&= E_{b1}\mathcal{A}\gamma_{b2}^2+\sqrt{E_{b1}^2\mathcal{A}\gamma_{b2}^4 - (m_{b1}^2 - m_{h}^2)\gamma_{b2}^2}\notag\\
&\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}}\\
\end{align}

The fitting procedure additionally modifies the masses of the b-jets as (equation \ref{eqn:kinfit_bjetmass})
\begin{equation}\label{eqn:kinfit_bjetmass}
m_{b_{1,2}}^{fit} = m_{b_{1,2}}\frac{E_{b_{1,2}}^{fit}}{E_{b_{1,2}}}
\end{equation}

For each b-jet a $\chi^2$ term is calculated as $\chi_{b1,2}^2 = \frac{E_{b1,2}^{fit}-E_{b1,2}^{meas}}{\sigma_{b1,2}}$.

@@

The measured recoil is (equation \ref{eqn:kinfit_recoilmeas})

\begin{equation}\label{eqn:kinfit_recoilmeas}
\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,H}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},b_{1}}}^{\text{meas}} - \vec{p_{\text{T},b_{2}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}}
\end{equation}

With the recoil from the fit (equation \ref{eqn:kinfit_recoilfit})
\begin{equation}\label{eqn:kinfit_recoilfit}
\vec{p_{\text{T,recoil}}}^{fit} = -\vec{p_{\text{T,H}}}^{fit} = - \vec{p_{\text{T},b_{1}}}^{fit} - \vec{p_{\text{T},b_{2}}}^{fit} - \vec{p_{\text{T},\Pgt_1}}^{fit} - \vec{p_{\text{T},\Pgt_2}}^{fit}
\end{equation}

A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as (equation \ref{eqn:kinfit_recoilchi2})

\begin{equation}\label{eqn:kinfit_recoilchi2}
\chi^2_{\text{recoil}} = (\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})^T V_{\text{recoil}}^{-1}(\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})
\end{equation}

where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as in equation \ref{eqn:kinfit_recoilcov} from the covariance matrices of the b-jets and
the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET (OBJECT RECO),
while the covariance matrices of the b-jets can be written in terms of position, momentum and resolution of the b-jets.

\begin{equation}\label{eqn:kinfit_recoilcov}
V_{\text{recoil}} = V_{\vec{p_{\text{T,miss}}}} - V_{b_{1}} - V_{b_2} 
\end{equation}

The total $\chi^2$ term that needs to be minimised in the fit can then be written as (equation \ref{eqn:kinfit_chitot})

\begin{equation}\label{eqn:kinfit_chitot}
\chi^2 = \chi^2_{b_1} + \chi^2_{b_2} + \chi^2_{\text{recoil}}
\end{equation}

The result of the kinematic fit are the tau and b-jet 4-vectors with their energies and momenta
set to the best fit values found for them in the fit. These can then be added together to find
the mass of the heavy Higgs boson as reconstructed by the kinematic fit.

@@

\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category, the total
yield after the initial event selection (before subdividing into categories) as
estimated in \Ztautau Monte Carlo samples is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from \ttbar backgrounds in the embedded
sample is accounted for by subtracting this contamination, as evaluated using
the dedicated \ttbar embedded samples, from the \Ztautau background.

\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using Monte Carlo samples.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the taus. In this control region
a data-to-Monte Carlo scale factor is estimated and applied to the yield estimate from Monte Carlo.

\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT to
be less than 30 GeV. To estimate the remaining contribution
from \Wjets in the signal region a sideband with \mT greater
than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high \mT to low \mT
extrapolation factor is determined from the \Wjets Monte Carlo
samples. The yield in the signal region is then the other-background-subtracted
data yield in the high \mT region multiplied by this extrapolation factor.
In the 2jet-2tag, a slightly different high \mT sideband of 60-120 GeV is used 
to give larger statistics for the \Wjets estimate after other backgrounds are
subtracted. The method of extrapolating this yied estimate into
the signal region is otherwise analogous.

The \Wjets shape is taken from the Monte Carlo samples. To 
increase the statistics for this estimate, the b-tagging definition
in the 2jet-1tag and 2jet-2tag categories is loosened to the loose (instead of medium)
working point for the purposes of shape estimation.

@@

\subsection{Other backgrounds}
\label{sec:hhh_backgrounds_other}
The remaining backgrounds of \Zellell, di-boson and single-top
events are small. Both shape and normalisation are
estimated using Monte Carlo samples.

@@

Remaining backgrounds from \ZZ, triboson and \ttbar\PZ production are estimated using
Monte Carlo samples. Backgrounds from \PZ+jets %($\ell\ell\tautau$ channel) 
and \WZ+jets %($\ell\ell\mutau$ and $\ell\ell\etau$ channels) 
events, with at least one misidentified lepton, are estimated from control regions in data.

@@

\subsection{Signal extraction}
\label{sec:hhh_results_extraction}

>>>>

\section{Datasets and \acl{MC} samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 $p-p$ 
running period of the LHC. 
Signal and background events were generated using several different \ac{MC} event generators. The \texttt{MadGraph}
\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
events. In addition to samples with a mixture of jet multiplicities ('inclusive' samples), samples binned in jet multiplicity
were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
in signal regions with multiple jets. The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
interactions.

@@

%Figure \ref{fig:Hhh_selection_kinematics_mt} shows some of the kinematic variables 
%of di-\Pgt candidates in the \mutau channel
%\begin{figure}[h!]
%\begin{center}
% \subfloat[Muon \pT]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_mt_2012.pdf}}
%  \subfloat[Hadronic \Pgt \pT ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_mt_2012.pdf}}~\\
%  \subfloat[Muon $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_mt_2012.pdf}}
%  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_mt_2012.pdf}}~\\
%
%\end{center}
%\caption{Plots of muon and hadronic \Pgt \pT and $\eta$ in the \mutau channel.}
%\label{fig:Hhh_selection_kinematics_mt}
%\end{figure}

@@

Figure \ref{fig:Hhh_selection_kinematics_etmt} shows some of the kinematic variables 
of di-\Pgt candidates in the \etau and \mutau channels
\begin{figure}[h!]
\begin{center}
 \subfloat[Electron \pT (\etau)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_1_2jetinclusive_et_2012.pdf}}
  \subfloat[Hadronic \Pgt \pT (\mutau)]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/pt_2_2jetinclusive_mt_2012.pdf}}
%  \subfloat[Electron $\eta$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_1_2jetinclusive_et_2012.pdf}}
%  \subfloat[Hadronic \Pgt $\eta$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/eta_2_2jetinclusive_et_2012.pdf}}~\\

\end{center}
\caption{Plots of electron \pT in the \etau channel and hadronic \Pgt \pT in the \mutau channel.}
\label{fig:Hhh_selection_kinematics_etmt}
\end{figure}

\subsection{Categorisation}
\label{sec:hhh_selection_categories}
ADD b-jet plots?
In both channels an selection on the transverse mass \mT between the electron/muon
and missing transverse energy, defined as in equation \ref{eqn:hhh_selection_mt}, is applied.
\begin{equation}\label{eqn:hhh_selection_mt}
m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}
\end{equation}
In this eqation \pT is the transverse momentum of the electron or muon, and $\Delta\phi$ the angle
between the light lepton and the missing transverse energy. The \mT distributions for the \etau
and \mutau channels, using the selections as
described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
is shown in figure \ref{fig:Hhh_selection_mt}

@@

\section{Data to \acl{MC} correction factors}
\label{sec:hhh_datamc}
\ac{MC} samples are used for the estimation of some of the backgrounds and the signal, 
and it is therefore important to correct for any mismodelling. The data to \ac{MC} 
correction factors used for this are estimated in dedicated control regions.

A reweighting is applied to make the pile--up distribution in \ac{MC}
match the distribution observed in data.DESCRIPTION

Data and \ac{MC} identification, isolation, and trigger efficiencies
are measured for electrons, muons and hadronic taus. The difference between
the efficiencies in data and \ac{MC} are applied to \ac{MC} events as a
scale factor $SF = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.

@@

In the \etau channel a data to \ac{MC} scale factor is applied
to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
fake rate between data and \ac{MC}. DERIVED HOW

To correct for the difference in b--tagging efficiency and light jet mis--tagging
rates between data and \ac{MC} \pT and $\eta$ dependent scale factors are 
derived using the method described in \cite{BTV8TeV}. There are separate scale factors for 
b-/c- jets and light jets. There are multiple possible ways to apply these
scale factors, for this analysis this is done through a promote/demote method.

In this method a demotion or promotion probability is assigned to every
jet as in equation \ref{eqn:promotedemote}.
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1}
\end{align}.
In this equation $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
in consideration.

@@

Before the fit, from the mass constraint we have (equation \ref{eqn:kinfit_prefit})
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_prefit}
m_{h}^2 &= E_{h}^2 - \vec{p_{h}}^2 = (E_{b1}+E_{b2})^2 - (\vec{p_{b1}} + \vec{p_{b2}})^2 \notag\\
& = 2E_{b1}E_{b2} + m_{b1}^2 +m_{b2}^2 - 2\vec{p_{b1}}\vec{p_{b2}} \notag\\
& = m_{b1}^2 +m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta_{b2}})\notag\\
&\Rightarrow (1-\vec{\beta_{b1}}\vec{\beta_{b2}}) = \frac{m_h^2 - m_{b1}^2 - m_{b2}^2}{2E_{b1}E_{b2}}
\end{align}
When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{b1}}\vec{\beta_{b2}})$ 
and equation \ref{eqn:gamma_def}:
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:gamma_def}
\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2}
\end{equation}
We get:
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_variation}
m_h^2 &= m_{b1}^2 + m_{b2}^2 - 2E_{b1}E_{b2}(1-\vec{\beta_{b1}}\vec{\beta{b2}}\notag\\
&= m_{b1}^2 +\frac{E_{b2,fit}^2}{\gamma_{b2}^2} +2\mathcal{A}E_{b1}E_{b2,fit}\notag\\
\Rightarrow E_{b2}^{fit}& = \frac{(-2E_{b1}\mathcal{A} + \sqrt{4E_{b1}^2\mathcal{A} - 4(m_{b1}^2-m_{h}^2)\gamma_{b2}^{-2}})\gamma_{b2}^2}{2}\notag\\
&= E_{b1}\mathcal{A}\gamma_{b2}^2+\sqrt{E_{b1}^2\mathcal{A}\gamma_{b2}^4 - (m_{b1}^2 - m_{h}^2)\gamma_{b2}^2}\notag\\
&\Rightarrow E_{b2}^{fit} = E_{b1}\mathcal{A}\gamma_{b2}^2(-1 + \sqrt{1+\frac{m_{h}^2 - m_{b1}^2}{E_{b1}^2\mathcal{A}\gamma_{b2}^2}}\\
\end{align}

The fitting procedure additionally modifies the masses of the b-jets as (equation \ref{eqn:kinfit_bjetmass})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_bjetmass}
m_{b_{1,2}}^{fit} = m_{b_{1,2}}\frac{E_{b_{1,2}}^{fit}}{E_{b_{1,2}}}
\end{equation}
For each b-jet a $\chi^2$ term is calculated as $\chi_{b1,2}^2 = \frac{E_{b1,2}^{fit}-E_{b1,2}^{meas}}{\sigma_{b1,2}}$.

@@

The measured recoil is (equation \ref{eqn:kinfit_recoilmeas})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilmeas}
\vec{p_{\text{T,recoil}}}^{\text{meas}} = -\vec{p_{\text{T,H}}}^{\text{meas}} = -\vec{p_{\text{T,miss}}}^{\text{meas}} - \vec{p_{\text{T},b_{1}}}^{\text{meas}} - \vec{p_{\text{T},b_{2}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_1^{\text{vis}}}}^{\text{meas}} - \vec{p_{\text{T},\Pgt_2^{\text{vis}}}}^{\text{meas}}
\end{equation}
With the recoil from the fit (equation \ref{eqn:kinfit_recoilfit})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilfit}
\vec{p_{\text{T,recoil}}}^{fit} = -\vec{p_{\text{T,H}}}^{fit} = - \vec{p_{\text{T},b_{1}}}^{fit} - \vec{p_{\text{T},b_{2}}}^{fit} - \vec{p_{\text{T},\Pgt_1}}^{fit} - \vec{p_{\text{T},\Pgt_2}}^{fit}
\end{equation}
A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as (equation \ref{eqn:kinfit_recoilchi2})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilchi2}
\chi^2_{\text{recoil}} = (\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})^T V_{\text{recoil}}^{-1}(\vec{p_{\text{T,recoil}}}^{\text{fit}} - \vec{p_{\text{T,recoil}}}^{\text{measured}})
\end{equation}
where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as in equation \ref{eqn:kinfit_recoilcov} from the covariance matrices of the b-jets and
the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET (OBJECT RECO),
while the covariance matrices of the b-jets can be written in terms of position, momentum and resolution of the b-jets. 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilcov}
V_{\text{recoil}} = V_{\vec{p_{\text{T,miss}}}} - V_{b_{1}} - V_{b_2} 
\end{equation}
The total $\chi^2$ term that needs to be minimised in the fit can then be written as (equation \ref{eqn:kinfit_chitot})
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_chitot}
\chi^2 = \chi^2_{b_1} + \chi^2_{b_2} + \chi^2_{\text{recoil}}
\end{equation}
The result of the kinematic fit are the tau and b-jet 4-vectors with their energies and momenta
set to the best fit values found for them in the fit. These can then be added together to find
the mass of the heavy Higgs boson as reconstructed by the kinematic fit.

@@

\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category, the total
yield after the initial event selection (before subdividing into categories) as
estimated in \Ztautau \ac{MC} samples is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from \ttbar backgrounds in the embedded
sample is accounted for by subtracting this contamination, as evaluated using
the dedicated \ttbar embedded samples, from the \Ztautau background.

\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the taus. In this control region
a data-to-\ac{MC} factor is estimated and applied to the yield estimate from \ac{MC}.

\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT to
be less than 30 GeV. To estimate the remaining contribution
from \Wjets in the signal region a sideband with \mT greater
than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high \mT to low \mT
extrapolation factor is determined from the \Wjets \ac{MC} 
samples. The yield in the signal region is then the other-background-subtracted
data yield in the high \mT region multiplied by this extrapolation factor.
In the 2jet-2tag, a slightly different high \mT sideband of 60-120 GeV is used 
to give larger statistics for the \Wjets estimate after other backgrounds are
subtracted. The method of extrapolating this yied estimate into
the signal region is otherwise analogous.

The \Wjets shape is taken from the \ac{MC} samples. To 
increase the statistics for this estimate, the b-tagging definition
in the 2jet-1tag and 2jet-2tag categories is loosened to the loose (instead of medium)
working point for the purposes of shape estimation.

@@

\subsection{Other backgrounds}
\label{sec:hhh_backgrounds_other}
The remaining backgrounds of \Zellell, di-boson and single-top
events are small. Both shape and normalisation are
estimated using \ac{MC} samples.

@@

Remaining backgrounds from \ZZ, triboson and \ttbar\PZ production are estimated using
\ac{MC} samples. Backgrounds from \PZ+jets %($\ell\ell\tautau$ channel) 
and \WZ+jets %($\ell\ell\mutau$ and $\ell\ell\etau$ channels) 
events, with at least one misidentified lepton, are estimated from control regions in data.

@@

\subsection{Signal extraction}
\label{sec:hhh_results_extraction}
The kinematic fit mass $m_{H}^{\text{kinfit}}$ is used as the discriminating variable.
For each channel and category, the compatibility of the $m_{H}^{\text{kinfit}}$ distribution
of the observed data with the expected background distribution can be assessed. All bins
of the $m_{H}^{\text{kinfit}}$ distribution are used to perform a shape analysis. The 
methods used for this were developed by the LHC Higgs Combination Group \cite{LHCHComb2011} 
and are used for all Higgs analyses in ATLAS and CMS.

For the data a likelihood function is constructed as (equation \ref{eqn:hhh_likelihood}).
\begin{equation} \label{eqn:hhh_likelihood}
\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot \Sigma_j p(~\theta_j|\theta_j)
\end{equation}

Where $\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given as (equation \ref{eqn:hhh_poisson})

\begin{equation}\label{eqn:hhh_poisson}
\text{Poisson}(n_{\text{data},i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))}
\end{equation}

The first term integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
in all channels and categories. $s$ represents the number of expected signal events
in each bin, and $b$ the number of expected background events. These are functions of 
$\theta$, the full set of nuisance parameters. The systematic uncertainties discussed in section 
REFERENCE are represented by a nuisance parameter $\theta_j$. The signal strength
modifier $\mu$ can represent different quantities depending on the normalisation of the 
signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
to 1 pb, so the signal strenght modifier represents
the cross-section $\times$ branching ratio of a possible signal.

IMPROVE THIS:
The second term $p(~\theta|\theta)$ represents the pdf of the uncertainty on the nominal
value of the nuisance parameter $~\theta$.

To compare the data with the background only and signal + background hypothesis, a test
statistic $~q_{\mu}$ can be defined. This is a single 
number that is used to distinguish between the two hypotheses. The test
statistic used for LHC Higgs analyses, known as the profile likelihood, is given 
in equation \ref{eqn:hhh_profilelikelihood}.

\begin{equation}\label{eqn:hhh_profilelikelihood}
q_{\mu} = -2\text{ln}\frac{\mathcal{L}(data|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})}
\end{equation}

Where we require $0 \leq \hat{\mu} \leq \mu$.

In this equation $\mu$ is the signal strenght modifier being tested, $\hat{\theta_{\mu}}$ denotes the values of the
nuisance parameters which maximise the likelihood for that particular $\mu$, while $\hat{mu}$ and $\hat{\theta}$ are
the values of signal strength modifier and nuisance parameters which give the global maximum of the likelihood.
The requirements on $\mu$ ensure that the signal strenght is non-negative ($ 0 \leq \hat{\mu}$) and that
a one-sided confidence interval is constructed so as not to allow the observation of  a 
signal with strength $\hat{mu} > \mu$ to cause rejection of the signal hypothesis ($ \hat{\mu} \leq \mu$).

Describe pdfs

The p-value for $\mu$ and for background-only ($\mu = 0$) can be determined as in equation \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}.

\begin{equation}\label{eqn:hhh_pvaluesig}
p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \Integral_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu}
\end{equation}

\begin{equation}\label{eqn:hhh_pvaluebkg}
1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \Integral_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} 
\end{equation}

$CL_s$ is then defined as (equation \ref{eqn:hhh_cls})

\begin{equation}\label{eqn:hhh_cls}
CL_s(\mu) = \frac{CL_{s+b}}{CL_b} = \frac{p_{\mu}}{1-p_b}
\end{equation}

The value of $\mu$ for which $CL_s(\mu) \leq \alpha$ then gives the upper limit 
In the case of the analysis discussed in this chapter, the value of $\mu$ for which the upper 
limit on cross-section times branching ratio for the \Htohhtobbtautau process reaches $1-\alpha$ is 
said to be excluded at a confidence level of $\alpha$. Upper limits at the LHC are generally
quoted at 95\% confidence level, therefore the upper limit on cross-section times branching ratio
for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
equals 0.05. MODIFIED FREQUENTIST APPROACH.
